### 2016-02-22 main text/draft0.0.tex
Adding 1D SOM res. for M31

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

@@

\begin{abstract} 
 The vast availability of data for nearby galaxies makes them suitable targets for data mining in order to find new patterns in these galaxies.
In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups using unsupervised self organizing map (SOM) method.
%We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other. 
%As a result, we can predict some properties of regions in other galaxies by having only few data.

@@

\section*{ACKNOWLEDGMENTS}
S.R and P.B acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining.bib}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand{\sii}{S~{\textsc II}\ } 
\newcommand{\oiii}{O~{\textsc III}\ } 
\newcommand{\hi}{H~{\textsc I}\ }

\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

@@

\begin{abstract} 
 The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis in order to find new patterns in these galaxies.
In this project we are studying data from 10 regions in M31 and 8 regions in M101.Based on available information for these two galaxies we classified these regions in different groups using unsupervised self organizing map (SOM) method.
%We divided these regions from 2 to 6 different classes, and for each class we are going to interpret results and check whether these classiﬁcations have a physical meaning or they are just statistically relate to each other. 
%As a result, we can predict some properties of regions in other galaxies by having only few data.

@@

\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining.bib}

### 2016-02-22 sections/data0.0.tex
Adding M101 regions
Adding 1D SOM res. for M31

%Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: region in m31}) and 8 regions in M101 (Fig~\ref{fig: region in m101}).
Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.

@@

@@

     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [SII] continuum and [OIII} continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) emission data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.

%M101 data: observed ones;
    \subsection{M101 data}
     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS24 and 70~$\mu$m~\cite{Dale09}, and  PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
     Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
     SFR(FUV + 24$\mu$m), stellar and total gas map were calculated followed method described in \cite{Rahmani16} to create these maps.

>>>>

%Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: regions in m31}) and 8 regions in M101 (Fig~\ref{fig: regions in m101}).
Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.

@@

\begin{figure}
   \begin{subfigure}[b]{0.5\textwidth}
        \centering
    %\centering
        \includegraphics[width=0.97\textwidth]{../images/M31/M31_3.png}
        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
        \label{fig: regions in m31}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images/M101/M101.png}
        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
    \label{fig: regions in m101}
    \end{subfigure}
\end{figure}

@@

     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] continuum and [\oiii] continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass, and total infrared (TIR) emission data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.

%M101 data: observed ones;
    \subsection{M101 data}
     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.
     Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
     SFR(FUV + 24$\mu$m), stellar and total gas map were calculated followed method described in \cite{Rahmani16} to create these maps.

### 2016-02-22 sections/method0.0.tex
Adding 1D SOM res. for M31

 \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail. In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.

@@

     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     SOM in {\tiny NNT} works in two phases. 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 which is a default value for the learning factor. 
     The ordering phase continues for requested number of iterations and during that steps changes the parameters in the way that in the last iteration learning factor is 0.02 and the neighbourhood distance is 1.

@@

 \subsection{Test Model}
 \label{sec: test model}
 %the sole puprpes of this section is to show how to read the SOM results. 
    Before we start creating SOM for our data, we apply this model on an already studied sample. 
    Our test sample contains spectral energy distribution (SED) as well as properties such as age, stellar mass and specific star formation rate of 142 galaxies with redshift 0.5 $ \leq$ Z $\leq $ 1, which were measured and studied by \cite{Hossein12}. 
   % \cite{Hossein12} used supervised neural network method to classify galaxies' spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
    We used SOM to group galaxies based on their SED. For each galaxy, fluxes on different wavelengths were an input of the program.

@@

    The colour between neurons with 34 galaxies and neurons with 54 galaxies is black, which indicate these two neurons have a maximum distance from each other and galaxies in those neurons are the least similar ones. By looking at the average SED plots for those two neurons, one can clearly see that the averaged SED of these two groups of galaxies are completely different. %should I talked about what kind of SED are they.
    On the other hand, the colour between neurons with 54 galaxies and 29 galaxies is yellow, which shows the similarity and closeness of galaxies in these two neurons. 
    Again, by looking at the average SED plots (c and d), it is clear that the averaged SED of these two groups are the most similar ones. 
    In Fig~\ref{fig: sed_testmodel2by2} plots (a) and (b) shows some similarity, if we look at the distance map (Fig~\ref{fig: testmodel2by2}) we could see colours between neurons related to these two groups is bright orange which is relatively bright which represents some similarity between these two groups.

@@

    One can increase the grids of the maps to the point that each neurons contain max 1 galaxy. 
    This situation eventually happens because no two galaxies are exactly alike.
    Even in this case, galaxies with similar SED stay in a area which all the neurons are connected with yellow colour, and the galaxies with different type of SED are separated from them with darker colours (Fig~\ref{fig: testmodel3}). 
    Note that, empty neurons in the SOM results have their weight vectors and if we apply this network on the other set of data, based on similarity of the new data set to our sample, they could sit in the empty neurons.

    \begin{figure}
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=0.7\textwidth]{../images/test_model/2by2_nei3.pdf}
            \caption{A combination of the hits and distance map in $2\times2$ SOM. }
             \label{fig: testmodel2by2}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth} 
            \centering
            \includegraphics[width=\textwidth]{../images/test_model/SED_total2by2nei3.png}
            \caption{An average SED of galaxies in  $2\times2$ gird.}
             \label{fig: sed_testmodel2by2}
        \end{subfigure}
        \caption{SOM result of the SED of the 142 galaxies in redshift of 0.5 $ \leq$ Z $\leq $ 1 with size of $2\times2$. Top: shows a combination of the hits and distance map in $2\times2$ SOM. Gray hexagonal shape areas represent neurons. Number of on each neurons shows the number of galaxies grouped in that neurons. Red lines connected neighbour neurons to each other, and colours between neurons are a scale of distance between neurons. Bottom: shows the Average SED of the galaxies in same neurons. Plots a, b, c, and d are averaged SED of galaxies in neurons with a number of 30, 29, 29, and 54, respectively.}
        \label{fig: testmodel1}

>>>>

 \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail. In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results. %PB20160218: contrast SOM with principal component analysis (PCA), which may be more familiar?

@@

     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
     SOM in {\tiny NNT} works in two phases. 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance (which is initially provided by user), and initial learning factor of 0.9 which is a default value for the learning factor. 
     The ordering phase continues for requested number of iterations and during that steps changes the parameters in the way that in the last iteration learning factor is 0.02 and the neighbourhood distance is 1.

@@

 \subsection{Test Model}
 \label{sec: test model}
 %the sole puprpes of this section is to show how to read the SOM results. 
    Before we start creating SOM for our data, we apply this model on an already studied sample. 
    Our test sample contains spectral energy distribution (SED) as well as properties such as age, stellar mass and specific star formation rate of 142 galaxies with redshift 0.5 $ \leq$ Z $\leq $ 1, which were measured and studied by \cite{Hossein12}. 
   % \cite{Hossein12} used supervised neural network method to classify galaxies' spectrum based on SED models from \cite{Kinney96} and \cite{Coleman80}.
    We used SOM to group galaxies based on their SED. For each galaxy, fluxes on different wavelengths were an input of the program. % PB20160218: should say how many data points per galaxy. Comment on the individual flux points not being statistically independent? Also, this is a fairly different sort of dataset than the M31 data, so need to explain how applicable.

@@

    The colour between neurons with 34 galaxies and neurons with 54 galaxies is black, which indicate these two neurons have a maximum distance from each other and galaxies in those neurons are the least similar ones. By looking at the average SED plots for those two neurons, one can clearly see that the averaged SED of these two groups of galaxies are completely different. %should I talked about what kind of SED are they. %PB: yes.
    On the other hand, the colour between neurons with 54 galaxies and 29 galaxies is yellow, which shows the similarity and closeness of galaxies in these two neurons. 
    Again, by looking at the average SED plots (c and d), it is clear that the averaged SED of these two groups are the most similar ones. 
    In Fig~\ref{fig: sed_testmodel2by2} plots (a) and (b) shows some similarity, if we look at the distance map (Fig~\ref{fig: testmodel2by2}) we could see colours between neurons related to these two groups is bright orange which is relatively bright which represents some similarity between these two groups.

@@

    One can increase the grids of the maps to the point that each neurons contain max 1 galaxy. 
    This situation eventually happens because no two galaxies are exactly alike.
    Even in this case, galaxies with similar SED stay in a area which all the neurons are connected with yellow colour, and the galaxies with different type of SED are separated from them with darker colours (Fig~\ref{fig: testmodel3}). 
    Note that, empty neurons in the SOM results have their weight vectors and if we apply this network on the other set of data, based on similarity of the new data set to our sample, they could sit in the empty neurons.
    %PB20160218: need some additional interpretation of the results
    \begin{figure}
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=0.7\textwidth]{../images/test_model/2by2_nei3.pdf}
            \caption{A combination of the hits and distance map in $2\times2$ SOM. }
             \label{fig: testmodel2by2}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth} 
            \centering
            \includegraphics[width=\textwidth]{../images/test_model/SED_total2by2nei3.png}
            \caption{An average SED of galaxies in  $2\times2$ gird.}
             \label{fig: sed_testmodel2by2}
        \end{subfigure}
        \caption{SOM result of the SED of the 142 galaxies in redshift of 0.5 $ \leq$ Z $\leq $ 1 with size of $2\times2$. Top: shows a combination of the hits and distance map in $2\times2$ SOM. Gray hexagonal shape areas represent neurons. Number of on each neurons shows the number of galaxies grouped in that neurons. Red lines connected neighbour neurons to each other, and colours between neurons are a scale of distance between neurons. Bottom: shows the Average SED of the galaxies in same neurons. Plots a, b, c, and d are averaged SED of galaxies in neurons with a number of 30, 29, 29, and 54, respectively.}
        \label{fig: testmodel1}
